Online Resource 1

### 2025-02-21 notebooks/Graphical_representation_alternatives.Rmd

---
title: 'Graphical representation example: Alternative interpretations'
output:
  html_document: 
    df_print:        paged
    code_folding:    hide
    toc:             yes
    toc_float:       yes
editor_options: 
  chunk_output_type: console
---

```{r setup}
library(knitr)
library(patchwork)
library(rstudioapi)

@@

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = TRUE,
  message  = FALSE,
  cache    = FALSE,
  dev      = "png",
  dpi      =   300,
  dev.args = list(type = "cairo-png")
)

# Output configuration options:
options(digits = 3)
```

>>>>

---
title: 'Graphical representation example: Alternative interpretations'
output:
  word_document:
    df_print:        kable
    toc:             yes
    reference_docx:  ../www/Notebook_template.docx
  html_document:
    df_print:        paged
    code_folding:    hide
    toc:             yes
    toc_float:       yes
editor_options:
  chunk_output_type: console
---

```{r setup}
#| echo: !expr 'knitr::is_html_output()'
library(knitr)
library(patchwork)
library(rstudioapi)

@@

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = is_html_output(),
  message  = FALSE,
  cache    = FALSE,
  dev      = "png",
  dpi      =   300,
  dev.args = list(type = "cairo-png")
)

# Output configuration options:
options(digits = 2)
```

### 2025-02-21 notebooks/example_script.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls()) 
library(pspline)
library(mvtnorm)
library(sn)
library(mnormt)
library(scatterplot3d)
library(copula)
library(ggplot2)
library(fungible)
library(pracma)
library(matlib)
library(rgl)
set.seed(123)
```

@@

Estos vectores tienen norma 1 y un ángulo entre ellos de `r round(matlib::angle(Base_1[,1],Base_1[,2]),2)` grados

@@

```{r angulos, include=FALSE}
alfa_1_1=matlib::angle(Base_1[,1],Base_C[,1])
alfa_1_2=matlib::angle(Base_1[,1],Base_C[,2])
alfa_2_1=matlib::angle(Base_1[,2],Base_C[,1])
alfa_2_2=matlib::angle(Base_1[,2],Base_C[,2])
```

@@

```{r , echo=FALSE, include=TRUE}
print(matlib::angle(Q[,1],Q[,2]))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls()) 
library(pspline)
library(mvtnorm)
library(sn)
library(mnormt)
library(scatterplot3d)
library(copula)
library(ggplot2)
library(fungible)
library(pracma)
library(rgl)
set.seed(123)

source("R/Math.R")
```

@@

Estos vectores tienen norma 1 y un ángulo entre ellos de `r round(angle(Base_1[,1],Base_1[,2]),2)` grados

@@

```{r angulos, include=FALSE}
alfa_1_1=angle(Base_1[,1],Base_C[,1])
alfa_1_2=angle(Base_1[,1],Base_C[,2])
alfa_2_1=angle(Base_1[,2],Base_C[,1])
alfa_2_2=angle(Base_1[,2],Base_C[,2])
```

@@

```{r , echo=FALSE, include=TRUE}
print(angle(Q[,1],Q[,2]))
```

### 2025-02-21 output/Cover_letter.Rmd

---
output:
  officedown::rdocx_document:
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../www/Template.docx
    number_sections: no
    keep_md:         no
editor_options: 
  chunk_output_type: console
---

September 5, 2024.

George A. Marcoulides \
Editor, *Educational and Psychological Measurement* \
University of California, Santa Barbara, USA

Dear Dr. Marcoulides:

Please find enclosed the manuscript entitled
*"A generalized definition of multidimensional item response theory
parameters"*,
which I am submitting for exclusive consideration of publication as an article
in Educational and Psychological Measurement.
Excluding the title page
(submitted separately according to Sage's guidelines),
the manuscript is 24 pages long and includes one figure and three tables.

@@

Our manuscript presents a generalization of the multidimensional IRT parameters
introduced by Reckase and Reckase & McKinley in their articles
["The difficulty of test items that measure more than one ability" (1985)][1]
and
["The discriminating power of items that measure more than one dimension"
(1991)][2],
respectively.
We believe that our results are still
an important contribution to modern measurement theory,
despite the long time since the publication of these articles.
Our generalization helps clarify the interpretation of
the multidimensional parameters while circumventing several issues
we have found in the literature regarding those multidimensional parameters,
due to implicitly applying them to monotonously non-increasing items and,
more importantly,
to a misconception of how these parameters should be computed and interpreted.
In the course of our research we have also found a crucial result regarding
the interpretation of the latent space and
its distinction from the so-called *test space*,
a duality of spaces almost completely overlooked in the literature,
but critical for understanding Multidimensional IRT and its connection with
the common factor model theory.
We also provide a method for accurately representing the items in vector form
in any test space (regardless of the covariance structure represented),
to help interpret and understand the multidimensional parameters.
We sincerely believe and hope you will find
the results we present in this manuscript interesting and fit for this journal.

@@

Daniel Morillo, Ph.D.\
Department of Behavioral Science Methodology \
Universidad Nacional de Educación a Distancia \
C. Juan del Rosal 10, Office 2.74 \
28040 Madrid, Spain

>>>>

---
output:
  officedown::rdocx_document:
    mapstyles:
      First Paragraph: Body Text
    base_format: bookdown::word_document2
    reference_docx: ../www/Template.docx
    number_sections: no
    keep_md:         no
editor_options: 
  chunk_output_type: console
---

September 16, 2024.

<br>

Sandip Sinharay, PhD \
Editor, *Psychometrika* \
Educational Testing Service, USA

<br>

Dear Dr. Sinharay:

Please find enclosed the manuscript entitled
*"A generalized definition of multidimensional item response theory
parameters"*,
which I am submitting for exclusive consideration of publication as an article
in Psychometrika.
Excluding the title page
(submitted separately according to Sage's guidelines),
the manuscript is 35 pages long and includes one figure and three tables.

@@

Our manuscript presents a generalization of the multidimensional IRT parameters
introduced by Reckase and Reckase & McKinley in their articles
["The difficulty of test items that measure more than one ability" (1985)][1]
and
["The discriminating power of items that measure more than one dimension"
(1991)][2],
respectively.
We believe that our results are still
an important contribution to modern measurement theory,
despite the long time since the publication of these articles.
Our generalization helps clarify the interpretation of
the multidimensional parameters while circumventing several issues
we have found in the literature regarding those multidimensional parameters,
due to implicitly applying them to monotonously non-increasing items and,
more importantly,
to a misconception about their computation and interpretation in applications
with non-identity covariance latent matrices.
In the course of our research we have also found a crucial result regarding
the interpretation of the latent space and
its distinction from the so-called *test space*,
a duality of spaces almost completely overlooked in the literature,
but critical for understanding Multidimensional IRT and its connection with
the common factor model theory.
We also provide a method for accurately representing the items in vector form
in any test space (regardless of the covariance structure represented),
to help interpret and understand the multidimensional parameters.
We sincerely believe and hope you will find
the results we present in this manuscript interesting and fit for this journal.

@@

Daniel Morillo, Ph.D.\
Department of Behavioral Science Methodology \
Universidad Nacional de Educación a Distancia (UNED) \
C. Juan del Rosal 10, Office 2.74 \
28040 Madrid, Spain

### 2025-02-21 output/ESM_1.Rmd

@@

::: {#refs}
:::

```{r empirical-table-Reckase2009-out}
#| cache:   false
#| tab.id:  empirical-table-Reckase2009-out
#| tab.cap: |
#|   Agnostic and covariance-based multidimensional item parameters in
#|   Reckase (2009), with an almost-rank-1 covariance matrix.
item_params_output
```

>>>>

```{r empirical-table-Reckase2009-out}
#| cache:   false
#| tab.id:  empirical-table-Reckase2009-out
#| tab.cap: |
#|   Agnostic and covariance-based multidimensional item parameters in
#|   Reckase (2009), with an almost-rank-1 covariance matrix
item_params_output
```

@@
